---
title: "Big Data Analytics Assignment 1"
output: html_notebook
---

## Q1

First I load the data files
```{r}
dat <- read.csv("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/migration2012.csv")
head(dat)
```

```{r}
states <- read.csv("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/states_chord.csv")
states
```

Next I reshape dat into the handful data format. I use **tidyr package** for the aim instead of **reshape package** because the foramer is the improved version of the latter.

```{r}
install.packages('tidyverse')
library(tidyverse)
```

```{r}
dat <- dat %>%
tidyr::gather(key=From, value=value, Alabama,Alaska,Arizona,Arkansas,California,Colorado,Connecticut,Delaware,District.of.Columbia,Florida,Georgia,Hawaii,Idaho,Illinois,Indiana,Iowa,Kansas,Kentucky,Louisiana,Maine,Maryland,Massachusetts,Michigan,Minnesota,Mississippi,Missouri,Montana,Nebraska,Nevada,New.Hampshire,New.Jersey,New.Mexico,New.York,North.Carolina,North.Dakota,Ohio,Oklahoma,Oregon,Pennsylvania,Rhode.Island,South.Carolina,South.Dakota,Tennessee,Texas,Utah,Vermont,Virginia,Washington,West.Virginia,Wisconsin,Wyoming)
```

Delete the puctuations.

```{r}
dat <- data.frame(apply(dat, 2, function(y) gsub("[[:punct:]]", " ", y)))
dat
```

Then I add two new columns to the above data frame.

```{r}
d1 <- merge(dat, states, by.x="From", by.y="States")
d1 <- d1[,c(-5,-6)]
names(d1)[4] <- "ID_From"

d2 <- merge(d1, states, by.x="To", by.y="States")
d2 <- d2[,c(-6,-7)]
names(d2)[5] <- "ID_To"
dat <- d2
dat
```

Sort the data frame in the ascending order

```{r}
dat <- arrange(dat, ID_From)
dat <- arrange(dat, ID_To)
dat
```

Convert the above data frame into the matrix form

```{r}
t1 <- dat[,c(1,2,4,5)]
t1 <- t1 %>%
  spread(key=To, value=ID_To)

t2 <- dat[,c(1,2,3,4)]
t2 <- t2 %>%
  spread(key=To, value=value)

t3 <- rbind(t1[1,],t2)
t3$From <- as.character(t3$From)
t3[1,2] <- 0
t3[1,1] <- "ID_To"
t3 <- t3 %>%
  arrange(ID_From)

library(data.table)
setcolorder(t3,c("From","ID_From","Connecticut","Maine","Massachusetts","New Hampshire","Rhode Island",
"Vermont","New Jersey","New York","Pennsylvania","Illinois","Indiana",
"Michigan","Ohio","Wisconsin","Iowa","Kansas","Minnesota",
"Missouri","Nebraska","North Dakota","South Dakota","Delaware","Florida",
"Georgia","Maryland","North Carolina","South Carolina","Virginia","District of Columbia",
"West Virginia","Alabama","Kentucky","Mississippi","Tennessee","Arkansas",
"Louisiana","Oklahoma","Texas","Arizona","Colorado","Idaho",
"Montana","Nevada","New Mexico","Utah","Wyoming","Alaska",
"California","Hawaii","Oregon","Washington"))

t3 <- t3[c(-1),c(-2)]

t4 <- t3[,-1]
rownames(t4) <- t3[,1]

t5 <- data.frame(apply(t4, 2, function(y) as.numeric(y)))
rownames(t5) <- t3[,1]
t5
```

Drawing the chord diagram
```{r}
library(chorddiag)

chorddiag(as.matrix(t5),groupColors=states$Color,showTicks=F,groupnamePadding=20,groupThickness=.05,groupnameFontsize=10)
```


## Q2

まだindividualを入れてないです。
Read "Stops On Lines" and the all GIS data of bus lines.
```{r}
library(dplyr)
library(sp)
library(rgdal)
library(leaflet)
library(ggmap)

# Bus Stops
SOL <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/BusStops1216","StopsOnLines1216")
SOL.pj <- spTransform(SOL, CRS("+proj=longlat +datum=WGS84"))

# Bus Routes
CC <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/ComCir1216","ComCir1216")
CC.pj <- spTransform(CC, CRS("+proj=longlat +datum=WGS84"))
LE <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/LimExp1216","LimExp1216")
LE.pj <- spTransform(LE, CRS("+proj=longlat +datum=WGS84"))
LCBD <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/LocalCBD1216","LocalCBD1216")
LCBD.pj <- spTransform(LCBD, CRS("+proj=longlat +datum=WGS84"))
LNCBD <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/LocalNonCBD1216","LocalNonCBD1216")
LNCBD.pj <- spTransform(LNCBD, CRS("+proj=longlat +datum=WGS84"))
RBRT <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/RapidBRT1216","RapidBRT1216")
RBRT.pj <- spTransform(RBRT, CRS("+proj=longlat +datum=WGS84"))

# とりあえずindividual2についてのみreadできることを確認。一旦放置してこれ以外でできるか試す。
I2 <- readOGR("/Users/susu/Desktop/Hong\ Kong/Semester2/Big_Data/assignment_data/as1/Individuals1216","2")
I2.pj <- spTransform(I2, CRS("+proj=longlat +datum=WGS84"))
```

make Line_list
```{r}
tmp_CC <- geometry(CC.pj)
tmp_LE <- geometry(LE.pj)
tmp_LCBD <- geometry(LCBD.pj)
tmp_LNCBD <- geometry(LNCBD.pj)
tmp_RBRT <- geometry(RBRT.pj)
tmps <- list(tmp_CC, tmp_LE, tmp_LCBD, tmp_LNCBD, tmp_RBRT)

Line_list <- list()
for (i in 1:5){
  for (j in 1:length(tmps[[i]])){
    Line_list <- c(Line_list, tmps[[i]][j]@lines[[1]]@Lines)
  }
}
```


make new_id
```{r}
pjs <- list(CC.pj, LE.pj, LCBD.pj, LNCBD.pj, RBRT.pj)
LinLSs <- list()
for (i in 1:5){
 LinLSs <- c(LinLSs, sapply(pjs[[i]]@lines, function(x) length(x@Lines)))
}
LinLSs <- LinLSs %>% unlist()

new_id <- sapply(1:length(LinLSs), function(x) paste0(x, "_", seq.int(LinLSs[[x]]))) %>% 
  unlist()
```

```{r}
## make a new data.frame (only route_id)
DAT=data.frame(matrix(rep(NA,1),nrow=1))[-1,]
for (i in 1:5){
  df <- data.frame(route_id = pjs[[i]]@data$VAR_IDENT)
  DAT <- rbind(DAT, df)
}
rownames(DAT) <- new_id

SLDF <- mapply(function(x, y) Lines(x, ID = y), x = Line_list, y = new_id) %>%
  #list() %>%
  SpatialLines() %>% 
  SpatialLinesDataFrame(data = DAT)
```


make new lines and LA map
```{r}
dat <- geocode('Los Angels')

leaflet() %>%
  setView(lng = dat['lon'], lat = dat['lat']	, zoom = 11) %>%
  addPolylines(data = SLDF, color = "black", opacity = 1, weight = 1) %>% 
  addCircles(data=SOL.pj@data,~LONG, ~LAT, color = "red", weight = 0.3) %>%
  addTiles()
```


## Q3

First I load the data.
```{r}
library(quantmod)
library(highcharter)

x <- getSymbols("AUD/JPY", src = "oanda", auto.assign = FALSE)
y <- getSymbols("GBP/USD", src = "oanda", auto.assign = FALSE)
```

Next make Bollinger's bands for each exchange rate.
```{r}
x.BBands.ll <- BBands(x)$dn
x.BBands.ul <- BBands(x)$up
x.BBands.m <- BBands(x)$mavg
y.BBands.ll <- BBands(y)$dn
y.BBands.ul <- BBands(y)$up
y.BBands.m <- BBands(y)$mavg
```

The drawing code is as follows.
```{r}
hc <- highchart(type="stock") %>% 
  hc_title(text="Charting Exchange Rates") %>% 
  hc_subtitle(text = "Data extracted using quantmod package") %>% 
  hc_yAxis_multiples(
    list(top = "0%", height = "50%", offset=0, opposite=TRUE),
    list(top = "50%", height = "50%", offset=0, opposite=TRUE)
  )%>%
  hc_add_series(x, id = "audjpy",name ="audjpy", yAxis=0, color="blue", lineWidth=1.5) %>%
  hc_add_series(x.BBands.ll, id = "audjpy.ll", name="audjpy Lower BBands",yAxis=0,
                color="black",dashStyle='shortdash', lineWidth=1) %>%
  hc_add_series(x.BBands.ul, id = "audjpy.ul", name="audjpy Upper BBands",yAxis=0,
                color="black",lineWidth=1) %>%
  hc_add_series(x.BBands.m, id = "audjpy.m",name="audjpy BBands MA", yAxis=0,
                color="red",lineWidth=1) %>%
  hc_add_series(y, id = "gbpusd",name="gbpusd",yAxis=1, color="green", lineWidth=1.5) %>%
  hc_add_series(y.BBands.ll, id = "gbpusd.ll",name="gbpusd Lower BBands", yAxis=1,
                color="black",dashStyle='shortdash',lineWidth=1) %>%
  hc_add_series(y.BBands.ul, id = "gbpusd.ul",name="gbpusd Upper BBands", yAxis=1,
                color="black",lineWidth=1) %>%
  hc_add_series(y.BBands.m, id = "gbpusd.m",name="gbpusd BBands MA", yAxis=1,
                color="red",lineWidth=1) %>%
  hc_add_theme(hc_theme_538())

hc
```


## Q4

Load libraries and check the raw data. And make ffdf after converting character columns to factor columns in original df.
```{r}
library(nycflights13)
library(ffbase)
library(ffbase2)
library(biglm)
library(pROC)
library(chron)

tmp <- flights
tmp$carrier <- as.factor(tmp$carrier)
tmp$tailnum <- as.factor(tmp$tailnum)
tmp$origin <- as.factor(tmp$origin)
tmp$dest <- as.factor(tmp$dest)

flightff <- as.ffdf(tmp)
```

Next I make new columns as follows
```{r}
flightff$Delay <- ffifelse(flightff$dep_delay > 0, 1,0)
flightff$DepHour <- flightff$hour
flightff$Car <- ffifelse(flightff$carrier %in% as.factor(c("DL","US","DH","UA")), 1, 0)
flightff$Night <- ffifelse(flightff$hour > 18 | flightff$hour < 6, 1, 0)
flightff$Weekend <- ffifelse(day.of.week(month=flightff$month, day=flightff$day, year=flightff$year) == 6, 1, 0)
```

I exclude the rows whose Delay values are NA and rename it to logitff.
And then I split the dataset into train set and test set.
```{r}
logitff <- flightff[!is.na(flightff$Delay),]

indx <- ff(1:nrow(logitff))
p <- 0.7
trainIndx <- ff(indx[1:trunc(length(indx)*p)])
trainset <- logitff[trainIndx,]
testIndx <- ff(indx[(trunc(length(indx)*p)+1):length(indx)])
testset <- logitff[testIndx,]
```

Logistic regression 
```{r}
fit <- bigglm.ffdf(Delay~DepHour+Car+Night+Weekend, data = trainset, family=binomial(), sandwich=TRUE)
summary(fit)
```

predict and make confusionmatrix in train_set
```{r}
train_pred <- predict(fit, newdata = trainset, type="response")
train_pred <- ifelse(train_pred>0.5, 1,0)
train_confusion <- table(as.integer(as.data.frame(trainset)$Delay), as.integer(train_pred))
train_confusion <- addmargins(train_confusion)
train_confusion
```

predict and make confusionmatrix in test_set
```{r}
test_pred <- predict(fit, newdata = testset, type="response")
test_pred <- ifelse(test_pred>0.5, 1,0)
test_confusion <- table(as.integer(as.data.frame(testset)$Delay), as.integer(test_pred))
test_confusion <- addmargins(test_confusion)
test_confusion
```























